\papertitle

### 2019-07-13 publications/18-whitepaper/article.tex
Trivial

\documentclass[a4paper, twocolumn]{article}
\newcommand{\papertitle}{Whitepaper: Community Development of Next Generation Storage and Compute Interfaces for Smart Workflow Processing}

@@

In this white paper, we describe the vision for the Next-Generation Interface (NGI) initiative that aims to tackle the aforementioned storage and compute challenges in a holistic approach.
Within the NGI consortium, we fuse state-of-the-art concepts into a revolutionary interface by rethinking how data-driven I/O should be done.
Basically, we believe workflows composed of data, compute and communication intensive tasks should drive the interfaces and hardware configurations to best support these programming models.
From the user perspective, NGI aims to provide an abstraction to data-driven processing and data management.
The NGI interface ultimately will increase the opportunity of implementations for smarter scheduling of compute and storage in heterogeneous environments considering characteristics of workflows and data.
From the system perspective, the vision of NGI aims to derive an execution plan that utilizes the available hardware and software infrastructure within and across data centers but also on small-scale systems.

@@

\section{Community Strategy}
\label{sec:community}

We are in the process to establish the NGI Forum that curates the development of the APIs.
The process will share the idea with the successful MPI Forum.
The approach is sketched in \Cref{fig:standardization};
members are experts from domain science, industry and data centers and form the bodies.
The activity is lead by the elected steering board.
Topic-specific workgroups and committees develop the standard (data model and APIs) driven by relevant use-cases encompassing the span from workflows to code snippets.
Ultimately, we will support the creation of a reference implementation based on state-of-the-art technology that demonstrates the approach on the use-cases.
We are aware that this endeavor is challenging; therefore, we won't expect that NGI 1.0 will include all features in the final version.
%We will settle on the set of features that the consortium identifies
%Similar to the way MPI 1.0 has grown, .

We expect that vendors and researchers will embrace the open ecosystem similarly to MPI and explore and contribute to the forum and its development.

\begin{figure}[b]
  \includegraphics[width=\columnwidth]{standardization}
  \caption{Organization of the NGI Forum}
  \label{fig:standardization}
\end{figure}

>>>>

\documentclass[a4paper, twocolumn]{article}
\newcommand{\papertitle}{Whitepaper: Smarter Workflow Processing with the Next Generation Data-Centric Interfaces}

@@

In this white paper, we describe the vision for the Next-Generation Data-Centric Interface (NGI) initiative that aims to tackle the aforementioned storage and compute challenges in a holistic approach.
Within the NGI consortium, we fuse state-of-the-art concepts into a revolutionary interface by rethinking how data-driven I/O should be done.
Basically, we believe workflows composed of data, compute and communication intensive tasks should drive the interfaces and hardware configurations to best support these programming models.
From the user perspective, NGI aims to provide an abstraction to data-driven processing and data management.
The NGI interface ultimately will increase the opportunity of implementations for smarter scheduling of compute and storage in heterogeneous environments considering characteristics of workflows and data.
From the system perspective, the vision of NGI aims to derive an execution plan that utilizes the available hardware and software infrastructure within and across data centers but also on small-scale systems.

@@
